Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-18 journal paper/content/conclusion.tex
Minor edits in open q.

\item \emph{Real-life data.}
Numerical experiments based on real-life datasets would arguably be more realistic. Bandit algorithms would probably need to incorporate \emph{contexts} (auxiliary signals available before each round), as the real-life bandit problems tend to be contextual.

@@

\noindent One difficulty with the last two directions is that the bandit ``side" of the model becomes considerably more complicated, both in terms of the rewards and in terms of the algorithms. Indeed, there are many reasonable ways to model a changing world (resp., contexts), and several  substantially different algorithmic approaches to deal with that. Even within the same approach, the distinctions between better and worse algorithms are not as clear, and the intuitions are not as well-established.

>>>>

\item \emph{Real-life data.}
Numerical experiments based on real-life datasets would arguably be more realistic. \asedit{To deal with real-life datasets, bandit algorithms would probably need to accommodate change over time and} \emph{contexts} (auxiliary signals available before each round).

@@

\noindent One difficulty with the last two directions is that the bandit ``side" of the model becomes considerably more complicated, both in terms of the rewards and in terms of the algorithms. Indeed, there are many reasonable ways to model a changing world (resp., dependence on  contexts), and several  substantially different algorithmic approaches to deal \asedit{these models. Consequently, the distinctions between better and worse algorithms are not as clear and well-established.}
